I need a title

### 2018-01-05 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

\begin{document}
\maketitle
\begin{abstract}
I need an abstract
aeuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuuu

% lncs keyword extension 
\keywords{hope, luke, ewoks}

@@

\hypertarget{unknowness}{%
\section{Unknowness}\label{unknowness}}

Requirements elicitation is the process of finding and formulation
requirements, and this process has many barriers due to stakeholders are
not able to express their needs, explain what they do and why,
conflicting demands, or new demands once other are met{[}1{]}, just to
mention some examples. Many analyst consider interviews the most
important elicitation technique, and usually elicitation process starts
with interviewing the stakeholders. Interviews allow analysts to check
their understanding about the problem domain inmediately and ask for
clarifications. Moreover, this technique is versatile in the sense of it
is possible that new and unexpected issues come up and they can be
attacked at that moment.

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
I need an abstract

% lncs keyword extension 
\keywords{I, need, keywords}

@@

\hypertarget{my-approach-i-need-a-section-title}{%
\section{My approach (i need a section
title)}\label{my-approach-i-need-a-section-title}}

\hypertarget{tacit-knowledge-in-elicitation-interviews}{%
\subsection{Tacit knowledge in elicitation
interviews}\label{tacit-knowledge-in-elicitation-interviews}}

Requirements elicitation is the process of finding and formulation
requirements, and this process has many barriers due to stakeholders are
not able to express their needs, explain what they do and why,
conflicting demands, or new demands once other are met{[}1{]}, just to
mention some examples. Many analyst consider interviews the most
important elicitation technique, and usually elicitation process starts
with interviewing the stakeholders. Interviews allow analysts to check
their understanding about the problem domain immediately and ask for
clarifications. Moreover, this technique is versatile in the sense of it
is possible that new and unexpected issues come up and they can be
attacked at that moment.

@@

\hypertarget{challenge-tacit-knowledge}{%
\subsection{Challenge tacit knowledge}\label{challenge-tacit-knowledge}}

The unknowness clarification presented in above suggest the presence of
three problems. The goal is to go from any scenario in which tacit
knowledge exists to known knowns. In order to achieve that goal and take
the advantages presented in elicitation interviews (immediately
clarification of assumptions and debate of implications) we are going to
use the theoretical framework described by Elrakaiby {[}3{]}. In this
framework we model the interview as a set of arguments and attacks
between them. In that sense, we will able to spot ambiguities and tacit
knowledge in terms of inconsistencies and insufficiency of information.
We will adapt some examples from {[}3{]} to show how each tacit
knowledge scenario can be addresed.

\textbf{known unknowns}: In the following example the domain knowledge
of the analyst is used to detect inconsistencies (attacks), because the
stakeholder didn't take into account relevant information about domain
application (location of trash bins).

A customers wants a recycling-support system and one of the goals is
\emph{to avoid fines from the municipality for incorrect recycling}.
According to the domain knowledge of the analyst, \emph{trash bins are
placed along the streets}. Thus, the goal is inconsistent with the
domain knowledge of the analyst because \emph{there is no way to trace
back person who brakes the recycling rule}. This scenario can be modeled
using arguments and attacks as follows:

The arguments: (A1)trash bins are placed along the streets, (A2)since
trash bins are placed along the streets, the trash owner cannot be
traced back. (B1)people who do not recycle should be fined (B2)to fine
people, the municipality must be able to trace products in trash bins
back to their owners.

Attacks: A2 attacks B1, and viceversa.

\textbf{unknown knowns}: In the following example analyst challenges the
stakeholder statement by using a question, as a result the stakeholder
reveals new information (reply).

A customers wants to develop a system to allow patients to measure the
amount of glucose in their blood, and then send the result to their
general practitioner. If the glucose level is above a certain threshold,
the practitioner pays a visit to the patient. The customer says:
\emph{In one-two days the doctor sees the notification in the system}.
Then analyst asks: \emph{What happens if the doctor is not available for
any reason?}. The customer replies: \emph{The general practitioner is
substituted by another doctor who accesses the same system}.

The arguments: (A1)in one-two days the doctor sees the
notification,(B1)the doctor might be unavailable,(B2)since the the
doctor might be unavailable, the notification might be delayed.

The attacks: A1 attacks B2, and viceversa

\textbf{unknown unknowns}: In the following example the stakeholder
didn't notice the inconsistency between his statements, but the analyst
did and asked for clarification. However, the stakeholder couldn't give
an answers due to his ignorance.

One of the customers wants to develop an app to manage medical-related
reservation in Tuscani. The costumer mentions that the \emph{current
reservation system, based on phone calls, was centralised}. During the
interview, the customer says that \emph{depending on where the
examination/visit will be, the patient has to call Nottola or Siena}.
The analyst could not understand how this realization was possible since
it means that the reservation system is not centralized. So the analyst
asks for clarification and the stakeholder cannot give any acceptable
answer.

The arguments: (A1)the current reservation is centralized, (B1)depending
on where the examination/visit will be (B2)the patience has to call
Nottola or Siena, (B3) since it is possible to call either Nottola or
Siena the system is not centralized.

The attacks: A1 attacks B3, and viceversa

\hypertarget{limits-of-elicited-knowledge}{%
\subsection{Limits of elicited
knowledge}\label{limits-of-elicited-knowledge}}

aeu
